---
title: "Assignment3"
author: "Lin Li"
date: "9/15/2019"
output: html_document
---


3.Copy the introductory example. The vector name stores the extracted names.
     R> name
     [1] "Moe Szyslak"       "Burns, C. Montgomery" "Rev. Timothy Lovejoy"
     [4] "Ned Flanders"      "Simpson, Homer"       "Dr. Julius Hibbert"

(a) Use the tools of this chapter to rearrange the vector so that all elements conform to thestandardfirst_name last_name.
```{r}
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson,Homer5553642Dr. Julius Hibbert"

library(stringr)

#Get all names
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))

#Remove second names
No_Alt_Names <- unlist(str_replace_all(name, pattern = "\\s.*[.]", replacement =""))

#Remove Titles
No_Titles <- unlist(str_replace_all(No_Alt_Names, pattern =".*[.]", replacement =""))

#Remove names separated by comma and a space
Name_FixSpace <- sub("(\\w+),\\s(\\w+)","\\2 \\1", No_Titles)

#Remove names separated by comma only
Name_Fix  <-sub("(\\w+),(\\w+)","\\2 \\1", Name_FixSpace)

#final output
Name_Fix
```

(b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.).

```{r}
str_detect(Name_Fix, "A-Za-z.")
```

(c) Construct a logical vector indicating whether a character has a second name.

```{r}
str_detect(Name_Fix, "/(/)")
```


4. Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.

(a) [0-9]+\\$ 

    any digit between 0 and 9 followed by $

   "45663$"

(b) \\b[a-z]{1,4}\\b

   matches the character "b", case sensitive with character length of 1 or 4

   "bark" or "b"

(c) .*?\\.txt$

    matches any character unlimited times followed by.txt (case sensitive) at the end

   "filename.txt"

(d) \\d{2}/\\d{2}/\\d{4}

   matches any 8 digits

   "12345678" or any"12575479"digits

(e) <(.+?)>.+?</\\1>

   matces any character enclosed by <> with any character enclosed by <> that is the same as the first

  &lt; 89 &gt; hello &lt; 89 &gt;
  
  
clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr
```{r}
secret <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
paste(unlist(str_extract_all(secret, "[[:upper:]]")), collapse = "")

```

